---
output: 
  revealjs::revealjs_presentation:
    theme: solarized
    css: styles.css
    includes:
        in_header: footer.html
    reveal_options:
        controls: false
        progress: false
        slidenumber: false
        loop: true
        autoSlide: 40000
---

```{r setup, include=FALSE}
library(tidyverse)
library(gganimate)
source(here::here("helper_funcs.R"))
knitr::opts_chunk$set(echo = FALSE, fig.height = 4)
options(gganimate.start_pause = 15)
```

```{r content, include = FALSE}
labs_all <- list(
  skills = c("Tidyverse-First Orientation",
             "Team Leader's Persistence",
             "Positive Learning Environment", 
             "Team's Enthusiasm for R",
             "Starting Level of R Knowledge")
)
```


## Upgrading to R: Tips and Mistakes I've Made

1. Excitement >> Skills
2. Failure's Coming, Get Ready
3. You are the Data Engineer your Team Needs
4. It Takes a Team to Write a Package
5. Git: Sometimes the Right Thing isn't the Easiest
6. Have you met my Friend RMarkdown?
7. Don't Get Too Excited Just Yet

## 1. Excitement >> Skills
```{r skills, messge = FALSE, warning =FALSE}
options(gganimate.nframes = 100, 
        gganimate.end_pause = 30)
labs <- labs_all$skills %>%
  stringr::str_wrap(20)

tibble(x = seq(length(labs)),
       pe = c(0.2, 0.33, 0.4, 0.7, 0.1),
       ymin = c(0.1, 0.15, 0.2, 0.4, -0.2),
       ymax = c(0.4, 0.4, 0.48, 0.9, 0.2),
       lab_y = c(0.8, 0.8, 0.8, 0.2, 0.8),
       lab = labs,
       time = x) %>%
  ggplot(aes(x = -x, y = pe, group = lab)) +
  geom_pointrange(aes(ymin = ymin, ymax = ymax)) +
  geom_text(aes(y = lab_y, label = lab), family = text_fam) +
  theme_rs() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  geom_hline(yintercept = 0, linetype = 2, color = "lightgrey") +
  ylab("Effect on Team's Productivity in R") +
  coord_flip(xlim = c(0.8, length(labs) + 0.2)) +
  transition_reveal(time) +
  enter_fade() +
  ease_aes('cubic-in-out')
```

## 2. Failure's Coming, Get Ready
```{r fail, messge = FALSE, warning =FALSE}
options(gganimate.nframes = 400,
        gganimate.end_pause = 10)
morale <- c(2, 3, 4.5, 3, 3, 2.6, 2.0, 0.5, 1.3, 2, 3.5, 4.0)
prod <- c(1, 2.5, 4, 3.5, 4, 3.5, 1.5, 0.5, 0.7, 1.2, 2.5, 3.5)
n <- 7

labs <- c("First day, discovered team works exclusively in Excel.",
          "Began first R project: Codename Tidy",
          "Codename Tidy development completed and delivered!",
          "Revelation: Codename Tidy never really code reviewed.",
          "Work continues apace on other projects.",
          "Discovered: Mistake in Codename Tidy. Poop.",
          "Decision: Team leader will totally rewrite code himself.",
          "Decree from Team Leader: Merge requests every single day.",
          "Observation: No merge requests this week. Mutiny underway?",
          "Realization: Team leader may have overreacted.",
          "Team Meeting: Design code review strategy with team.",
          "Observation: Team members bought in.")

days <- c(0, 1, 23, 24, 25, 26, 26.5, 28, 29, 30, 31, 40)

tibble(person = rep(seq(n), each = length(morale)),
       time = rep(seq(length(morale)), n),
       morale = morale + runif(n * length(morale)),
       prod = prod + runif(n * length(prod)),
       lab = rep(labs, n)) %>%
  mutate(lab = factor(lab, levels = labs, ordered = TRUE)) %>%
  ggplot() +
  geom_point(aes(y = morale, x = prod, color = factor(person)),
             size = 5,
             alpha = 0.8) +
  geom_line(aes(x = prod, y = morale, group = person),
            color = "lightgrey",
            alpha = 0.3) +
  ggtitle("Team's Log, Day {days[frame_along]} - {labs[frame_along]}") +
  theme_rs() +
  ylab("Individual Morale") +
  xlab("Individual Productivity") +
  guides(color = FALSE) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank()) +
  ggthemes::scale_color_solarized() +
  transition_reveal(time) +
  enter_fade() +
  exit_shrink() +
  ease_aes('sine-in-out')
```

## 3. You are the Data Engineer your Team Needs
```{r csvs, messge = FALSE, warning =FALSE}
options(gganimate.nframes = 100,
        gganimate.end_pause = 30)
labs <- c("Really enjoy data cleaning",
          "Appreciate reproducible data pipelines",
          "Wish someone else would build their data pipeline",
          "Would benefit if input data were cleaner",
          "Died from building ETL pipeline with CSVs")
make_bar_dat(c(0.2, 0.5, 0.5, 0.9, 0.0),
             labs,
             laby = c(0.3, 0.4, 0.6, 0.8, 0.15)) %>%
  bar_plot("Proportion of Data Scientists who...") +
  transition_reveal(x) +
  enter_fade() +
  ease_aes('cubic-in-out')
```

## 4. It Takes a Team to Write a Package
```{r pkg, messge = FALSE, warning =FALSE}
options(gganimate.nframes = 400,
        gganimate.end_pause = 10)
labs <- c("Dplyr Functions with Diagnostics",
          "Reference Data Sets",
          "Standard Plots",
          "openxlsx Wrappers with Formatting",
          "Special Analytical Functions",
          "Report Templates",
          "Vignettes",
          "Contributions from all Team Members",
          "Clever use of R in Package Name") %>%
  stringr::str_wrap(15)

pd <- tibble(labs = labs,
             x = seq(length(labs)),
             p = c(0.05, 0.1, 0.12, 0.15, 0.2, 0.22, 0.34, 0.65, 0.96)) %>%
  extend_end_state()

pd %>%
  ggplot(aes(x = x)) +
  geom_area(aes(y = p)) +
  geom_label(aes(label = labs, y = p + 0.05),
             family = text_fam, size = 4) +
  theme_rs() +
  ylab("Likelihood of Use") +
  ggtitle("What to add to youR package:") +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank()) +
  coord_cartesian(xlim = c(min(pd$x - 0.5), max(pd$x + 0.5))) +
  transition_reveal(time, keep_last = TRUE) +
  enter_fade() +
  ease_aes('cubic-in-out')
```

## 5. Git: Sometimes the Right Thing isn't the Easiest
```{r git, messge = FALSE, warning =FALSE}
options(gganimate.nframes = 400,
        gganimate.end_pause = 25)
labs <- c("I'm going to learn git!",
          '"Git is just a directed graph"...umm...',
          "Just add, commit, push. Simple!",
          "First merge request, booyah!",
          "Hrm, I messed something up.",
          "Aha, I'll clean it right up with `git reset --hard`",
          "Uh Oh.",
          "Oh No.",
          "Where's all my stuff?",
          "Took 3 hours, but I figured it out.",
          "Add, commit, push.",
          "Merge request!",
          "Code review on github!",
          "Comment on merge request!",
          "Rollback nonworking version!",
          "Out of the office, you can still get my code!")
pd <- tibble(wf = c(0, -0.4, 0.1, 0.2, 0, -0.5, 0, 0, 0,
                    0, 0.1, 0.15, 0.25, 0.4, 0.6, 0.9),
             cry = c(0, 0.05, 0.01, 0.01, 0.1, 0.05, 0.2, 0.3, 0.5, 0.6,
                     0.3, 0.1, 0.01, 0.01, 0.01, 0.01),
             time = seq(length(wf))) %>%
  gather(key = series, value = value, wf, cry) %>%
  mutate(series = case_when(series == "wf" ~ "Productivity",
                            series == "cry" ~ "Pr(Crying)"))

pd %>%
  ggplot(aes(y = value, x = time, group = series)) +
  geom_point(size = 1.5) +
  geom_line() +
  geom_hline(yintercept = 0, linetype = 2, color = "lightgrey") +
  theme_rs() +
  scale_y_continuous(labels = scales::percent) +
  geom_segment(aes(xend = max(pd$time) + 2, yend = value),
               linetype = 2, colour = 'grey') +
  geom_text(aes(x = max(pd$time) + 2, y = value, label = series),
            family = text_fam) +
  coord_cartesian(xlim = c(0, max(pd$time) + 3)) +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  xlab("Time") +
  ylab("Proportional Increase In") +
  ggtitle("Stages of Git - {labs[as.integer(frame_along)]}") +
  transition_reveal(time) +
  enter_fade() +
  ease_aes('cubic-in-out')
```

## 6. Have you met my Friend RMarkdown?
```{r rmd, message= FALSE, warning = FALSE}
options(gganimate.nframes = 100,
        gganimate.end_pause = 30)
labs <- c("easy to share output + code",
          "natural interweaving of code and commentary",
          "compiles to useful formats (html, word, slides, etc)",
          "custom templates in team's package",
          "can write chunks in SQL, Python, Stan, ...",
          "will render pie charts") %>%
  stringr::str_wrap(25)
pd <- tibble(lab = factor(labs, labs, ordered = TRUE),
             time = seq(length(labs)),
             val = c(0.3, 0.22, 0.20, 0.15, 0.119, 0.01),
             cv = cumsum(val),
             ypos = lag(cv, default = 0) + 0.5 * val) %>%
  mutate(ypos = ifelse(ypos > 0.98, 0.05, ypos))

pd <- lapply(seq(length(labs)), function(i) filter(pd, lab %in% labs[seq(i)]) %>%
               mutate(disp = i)) %>%
  bind_rows()

pd %>%
  ggplot(aes(x = 1, group = disp)) +
  geom_bar(aes(fill = lab, y = val), stat = "identity", position = "stack") +
  geom_label(aes(x = 1.7, y = ypos, label = lab), 
             family = text_fam, alpha = 0.8) +
  coord_polar("y", start = 0) +
  guides(fill = FALSE) +
  ggthemes::scale_fill_solarized() +
  theme_rs() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank()) +
  labs(caption = "I swear I've never made a pie chart in ggplot2 before and had to look up how.") +
  ggtitle("Reasons I Love RMarkdown") +
  transition_reveal(disp) +
  enter_fade() +
  ease_aes('cubic-in-out')
```

## 7. Don't Get Too Excited Just Yet
```{r tf}
labs <- c("Replace Excel Data Processing",
          "Dashboarding",
          "Preprocess Data for Tableau",
          "Run Stata Command from R",
          "Port Stata Command into R",
          "Linear Regression",
          "Anything that uses TensorFlow") %>%
  stringr::str_wrap(20)

norm <- function(x) (x - min(x)) / max(x)

pd <- crossing(use = seq(0, 1, 0.05),
               vis = seq(0, 1, 0.05)) %>%
  mutate(fill = norm(1 - ((vis * use) ^ 2 + use - vis)))
pd2 <- tibble(use = c(0.83, 0.8, 0.95, 0.6, 0.4, 0.5, 0.1),
              vis = c(0.1, 0.8, 0.45, 0.2, 0.05, 0.5, 0.95),
              lab = labs,
              time = seq(length(labs)))

pd %>%
  ggplot(aes(x = use, y = vis)) +
  geom_raster(aes(fill = fill)) +
  geom_label(data = pd2, aes(label = lab, group = time), family = text_fam) +
  scale_fill_gradient2(low = "green", mid = "grey", high = "red",
                       labels = scales::percent, midpoint = 0.5) +
  theme_rs() +
  xlab("Useful") +
  ylab("Sexy") +
  theme(legend.position = "bottom",
        axis.text = element_blank(),
        axis.ticks = element_blank()) +
  labs(fill = "Pr(No More R)") +
  ggtitle("Projects in First Year of R Adoption") +
  transition_reveal(time) +
  enter_fade() +
  ease_aes('cubic-in-out')
```







