---
title: "8 Tips for Upgrading to R"
author: "Alex Gold"
date: "1/10/2019"
output: 
  revealjs::revealjs_presentation:
    theme: league
---

```{r setup, include=FALSE}
library(tidyverse)
library(gganimate)
source(here::here("helper_funcs.R"))
knitr::opts_chunk$set(echo = FALSE)
```

## 8 Tips for Upgrading to R

{{sprintf("%s. %s", 1:8, tips) %>% paste(collapse = "\n")}}


## {{tips["skills"]}}
Relative importance of R skills vs Technical Skills at Start
Interest in Learning
Persistence of Team Lead

## {{tips["fail"]}}
Actual Productivity
Manager's Perceived Productivity
Team's Buy In 

Bug leads to error in deliverable, team lead insists whole team pushes to git EVERY DAY

## {{tips["csvs"]}}
```{r}
make_bar_dat(c(0, 0.01, 0.8), 
             c("Died from building an ETL pipeline out of CSV files", 
               "Are excited to give you money for infrastructure", 
               "Will notice if errors diminsh and velocity increases")) %>%
  bar_plot("Proportion of People")
```

## {{tips["package"]}}

Things to include:

* wrappers around functions with diagnostics
* commonly used data
* standard plots
* functions to write out spreadsheets
* special analytical functions
* Templates for use patterns (preprocessing, analysis)
* New project setup packages

Variable importance plot for Effect on use of package

Writing a vignette
Making sure people know why you care
Getting everyone on the team to contribute
Clever use of capital R in package name

## {{tips["git"]}}


How useful git is
How much longer it takes to learn than you want
Useful git help that starts with "well, if you just think of git as a..."

## {{tips["markdown"]}}

## {{tips["invisible"]}}

## {{tips["tf"]}}
